Testing Education State Transitions

### 2023-06-19 minos/testing/education_transitions.Rmd
Changed ages that people achieve certain education levels, and allowed transition into education_state==1 for people who achieve lower grades in GCSEs (or equivalent quals)

if (shall.we.save) {
  ggsave(filename = 'S7_labour_state.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_labour_state',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'education_state.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'education_state',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)

>>>>

ggsave(filename = 'S7_labour_state.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = TRUE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_labour_state',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'education_state.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'education_state',
                 save = TRUE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'education_state',
               save = TRUE,
               save.path = save.path)
